%!TeX program = pdflatex
% Brian Libgober's Curriculum Vitae
% Email: blibgober@ucsed.edu
% Web: https://brianlibgober.com/
% Repo: https://github.com/libgober/cv

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing
\usepackage[backend=biber,isbn=false,url=false,maxcitenames=50]{biblatex} %bib files
\usepackage[symbol]{footmisc} %cool footnotes
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
% what is your name?

\newcommand{\myname}{Brian Libgober}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{helvet}     % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    pdfauthor   = {\myname},
    pdfkeywords = {city planning, housing, street networks, transportation, urban design, urban informatics},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

%setup bibliography
    \addbibresource{LibgoberPublications.bib}

\DeclareCiteCommand{\citejournalarticle}
    {\usebibmacro{prenote}}
    {\usebibmacro{citeindex}%
    \usebibmacro{title}%
    \usebibmacro{journal}%
    \usebibmacro{doi+eprint+url}%
    \usebibmacro{author}.%
    }
    {\usebibmacro{postnote}}
    
\DeclareCiteCommand{\citeworkingpaper}
    {\usebibmacro{prenote}}
    {\usebibmacro{citeindex}%
    \usebibmacro{title}%
    \usebibmacro{doi+eprint+url}%
    \usebibmacro{author}.
    \usebibmacro{journal}
    }
    {\usebibmacro{postnote}}

%%%%%%%%%%%%%%% CUSTOM COMMANDS to AVOID MISTAKES

\newcommand{\talk}[4]{\item[#1]{\tab{}#3. \enquote{#2,} #4.}} %{year}{title}{location}{day}
    %\item[2020] \tab{}\enquote{Agency Failure and Individual Accountability,} Department of Political Science, Georgetown University, Jan 24.
\newcommand{\SPSA}{Southern Political Science Association (SPSA) Annual Conference}
\newcommand{\APSA}{American Political Science Association (APSA) Annual Conference}
\newcommand{\course}[5]{\item[#1] \tab{}#3 (#4). #5. #2.} %{year}{semester}{title}{level}{role} 



\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        School of Global Policy and Strategy \\
        University of California, San Diego
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \href{mailto:blibgober@ucsd.edu}{blibgober@ucsd.edu} \\
        +1 708 642 4741 \\
        \href{https://brianlibgober.com}{brianlibgober.com} \\
        %\href{https://github.com/libgober/cv/raw/main/cv-blibgober.pdf}{CV Latest Version}
    \end{minipage}
    

    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab{}Government, Harvard University, 2018
        \item[M.A.]  \tab{}Statistics, Harvard University, 2017
        \item[J.D.]  \tab{}University of Michigan Law School, \textit{cum laude}, 2015
        \item[B.A.]  \tab{}Mathematics and Philosophy, University of Chicago, \textit{with honors}, 2010

    \end{tablist}

    \section*{Appointments}

    \begin{tablist}

        \item[2020--]   \tab{}University of California, San Diego \\
                             Assistant Professor, School of Global Policy and Strategy

        \item[2018--20] \tab{}Yale University \\
                             Postdoctoral Associate, Department of Political Science \\ 

    \end{tablist}

    \section*{Research Summary}
    I research the political economy of American institutions, with a particular emphasis on regulation-making by executive agencies. The majority of American political scientists working on regulation focus on issues of separation of powers, political control, and oversight. By contrast, my work attends to issues of distribution and the often fraught relationship between regulators and lobbyists. More broadly, I explore themes of economic inequality, interest group power, and the design of legal and governmental institutions. Methodologically, I combine multiple approaches, including formal models, quantitative empirics, and case studies.
    
    \section*{Publications}

    \subsection*{Peer-Reviewed Journal Articles}
    \begin{tablist}
    \item[2020] \tab{}\citejournalarticle{Libgober2020}
    
    \item[2020] \tab{}\citejournalarticle{Libgober2020b}
    
    \item[2020] \tab{}\citejournalarticle{Carpenter2020}
    \end{tablist}
    
    \subsection*{Working Papers\footnote[2]{Drafts of all working papers are available at \href{https://brianlibgober.com}{https://brianlibgober.com}.}}
    \begin{tablist}
    \item[2021] \tab{}\citeworkingpaper{Abi-Hassan2021} (R\&R, \textit{Political Analysis})
    \item[2021] \tab{}\citeworkingpaper{Libgober2021} (R\R, PLOS: ONE)
    \item[2021] \tab{}\citeworkingpaper{Carpenter2021} 
    \item[2021] \tab{}\citeworkingpaper{Chen2021}
    \item[2021] \tab{}\citeworkingpaper{Jerzak2021}
    \item[2020] \tab{}\citeworkingpaper{Libgober2020c} %agencyfailure
    \item[2019] \tab{}\citeworkingpaper{Libgober2019a}
    \end{tablist}
    
    \subsection*{Work In Progress}
    
    \begin{tablist}
    \item[\the\year] \tab{}\citeworkingpaper{Libgober2021b}
    \item[\the\year] \tab{}\citeworkingpaper{Libgober2021a}
    \item[\the\year] \tab{}\citeworkingpaper{Li2021}
    \item[\the\year] \tab{}\citeworkingpaper{Bolotnyy2021}
    \end{tablist}

    \subsection*{Other Publications}
    \begin{tablist}
    \item[In Press]     \tab{}\citejournalarticle{Carpentera}
    \item[2020] \tab{}\citejournalarticle{Libgober2019}
    \item[2018] \tab{}\citejournalarticle{Carpenter2018}
    \item[2015] \tab{}\citejournalarticle{Libgober2015a}
    \end{tablist}
    
    \section*{Invited Talks}

    \begin{tablist}
    \talk{2020}{Agency Failure and Individual Accountability}{Georgetown University. Department of Government}{Jan 24}
    %
    \talk{2020}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{University of Texas, Austin. McCombs School of Business}{Jan 8}
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Stanford University. Hoover Institution}{Dec 6}
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Vanderbilt University. Department of Political Science}{Nov 13}
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{University of California, San Diego. School of Global Policy and Strategy}{Nov 6}
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Harvard Law School}{Nov 5}    
    %
    \talk{2019}{Agency Failure and Individual Accountability}{George Mason Law School}{Sep 19}
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Washington University in St. Louis. Department of Political Science}{Sep 17}    
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Berkeley Law School. Jurisprudence and Social Policy Program}{Feb 7}    
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Harvard Business School. Business Government and International Economy Unit}{Nov 5}   
    % 
    \talk{2019}{The Gains from Lobbying Financial Regulators}{Administrative Conference of the United States}{Aug 9}    
    %
    \talk{2018}{What’s at Stake in Rulemaking? Financial Market Evidence for Banks’ Influence on Administrative Agencies}{University of Texas, Austin. McCombs School of Business}{Mar 23}
    
    \end{tablist}

    \section*{Conference Activity}
    
    \subsection*{Conference Presentations}
    \begin{tablist}
    \talk{2021}{The Politics of Place: Evidence from Refugees to the US}{\APSA}{Oct 2}
    \talk{2021}{Ex Post Lobbying and the Dynamics of Legislative Attention}{\APSA}{Oct 1}
    \talk{2021}{Participatory Inequality and Rulemaking: Evidence from Financial Regulation}{\APSA}{Sep 30}
    \talk{2021}{Lawyers as Lobbyists}{American Political Economy Summer School}{Jul 1}
    \talk{2020}{One Voice: the Role of Organization in Lobbying}{\APSA}{Sep 10}
    \talk{2019}{Agency Failure and Individual Accountability}{Bureaucracy and Presidential Administration: Expertise and Accountability in Constitutional Government. George Mason Law School}{Dec 6}
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{American Law and Economics Association (ALEA) Annual Conference}{May 17}
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Southern Political Science Association (SPSA) Annual Conference}{Jan 18} 
    \talk{2018}{What Public Comments During Rulemaking Do (and Why)}{Midwest Political Science Association (MPSA) Annual Conference}{Apr 7}
    \talk{2018}{The Price of Votes}{Midwest Political Science Association (MPSA) Annual Conference}{Apr 5}
    \talk{2018}{What Public Comments During Rulemaking Do (and Why)}{Southern Political Science Association (SPSA) Annual Conference}{Jan 5} 
    \talk{2018}{Participation, Inequality, and Rational Responsiveness}{Southern Political Science Association (SPSA) Annual Conference}{Jan 4}    
    \talk{2017}{Lobbying with Lawyers: Financial Market Evidence for Banks’ Influence on Rulemaking}{Radcliffe Institute for Advanced Study}{Dec 8}
    \talk{2017}{Equities and Inequities in Financial Rulemaking}{Midwest Political Science Association (MPSA) Annual Conference}{Apr 6}
	\talk{2017}{Lawyering and Lobbying: Why Banks Shape Rules}{University of Chicago Booth Business School}{Mar 4}
	\talk{2015}{Accident Liability in Imperfectly Competitive Markets}{American Law and Economics Association (ALEA) Annual Meeting}{May 16}
    \end{tablist}
    
    \subsection*{Poster Sessions}
    \begin{tablist}
    \talk{2018}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Annual Conference on Empirical Legal Studies (CELS)}{Nov 9}
    \end{tablist}
    %\subsection*{Sessions Organized}

    \subsection*{Other Conference Participation}
    \begin{tablist}
    \talk{2021}{Lobbyists and Lobbying, Strategies and Goals}{\APSA}{Oct 3 (discussant)}    
    \talk{2021}{Politics of Rulemaking in the Administration State  }{\APSA}{Oct 1 (discussant)}    
    \talk{2021}{Legislative Productivity in the US}{\APSA}{Sep 29 (chair and discussant)}
    \talk{2021}{Separation of Powers and Interbranch Relationships}{\APSA}{Sep 30 (chair and discussant)}
    \talk{2021}{Advances in Law Enforcement Policy Research}{\APSA}{Sep 30 (chair)}
    \end{tablist}
    %\subsection*{Invited Panelist}

    %\subsection*{Conference Papers Presented}

    \section*{Departmental Talks}

    \begin{tablist}
    \talk{2020}{Does Electoral Politics Explain the Distribution of CDC Test Kits? Evidence from FOIA}{ University of California, San Diego. School of Global Policy and Strategy Junior Faculty Brownbag}{Oct 28}
    \talk{2018}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Harvard University. Political Economy Workshop}{Oct 29}
    %
	\talk{2018}{What Public Comments During Rulemaking Do (and Why)}{Harvard University. American Politics Research Workshop}{Feb 13}
    %
    \talk{2017}{Getting a Lawyer While Black: A Field Experiment}{Harvard University. Working Group in Political Psychology}{Mar 10}
    %
    \talk{2017}{Lawyering and Lobbying: Why Banks Shape Rules}{Harvard University. American Politics Research Workshop}{Feb 7}
    %
    \talk{2016}{Getting a Lawyer While Black: A Field Experiment}{Harvard University. Harvard Experiments Working Group}{Sep 9}
    %
    \talk{2016}{Getting a Lawyer While Black: A Field Experiment}{Harvard Law School. Law and Economics Seminar}{Mar 3}
    \end{tablist}
    
    
    \section*{Fellowships}
    
    \begin{tablist}
    \item[2016-18] \tab{}Stone PhD Scholar in Inequality and Wealth Concentration, Harvard Kennedy School.
    \item[2015] \tab{}Terence M. Considine Fellowship in Law and Economics, Harvard Law School.
    \item[2012-15] \tab{}Dean's Scholarship, University of Michigan Law School.
    \item[2006-10] \tab{}Viola Bower Merit Scholarship, University of Chicago.
    \end{tablist}

    \section*{Teaching}
    
    \subsection*{University of California San Diego}
    \begin{tablist}
    \course{2021}{Fall}{Policy Analysis and Social Welfare}{MPP/MIA}{Primary Instructor}
    \course{2021}{Fall}{Law and Administration}{MPP/MIA}{Primary Instructor}
    \course{2021}{Spring}{Law and Administration}{MPP/MIA}{Primary Instructor}
    \course{2021}{Spring}{Bureaucratic Politics}{MPP/MIA}{Primary Instructor}
    \course{2021}{Winter}{Interest Groups and the Policymaking Process}{MPP/MIA}{Primary Instructor}
    \end{tablist}
    
    \subsection*{Yale University}
    \begin{tablist}
    \course{2019}{Fall}{American Mass Media: Law, Politics, and Policy}{Undergraduate}{Primary Instructor}
    \course{2019}{Spring}{Money in Politics}{MPP/MIA}{Primary Instructor}
    \end{tablist}
    
    
    \subsection*{Harvard University}
    \begin{tablist}
    \course{2017}{Fall}{Formal Models of Domestic Politics}{PhD}{Teaching Assistant (Primary Instructor: Horacio Larreguy)}
    \course{2016}{Fall}{Bureaucratic Politics}{Undergraduate/Graduate}{Teaching Assistant (Primary Instructor: Daniel Carpenter)}
    \end{tablist}

    \subsection*{Massachussets Institute of Technology}
    \begin{tablist}
    \course{2015}{Spring}{Constitutional Law \& Judicial Politics}{PhD}{Course Assistant (Primary Instructor: Chris Warshaw)}
    \end{tablist}

   \subsection*{University of Michigan}

   \begin{tablist}
    \course{2013}{Fall}{Mass Media and Election Politics}{Undergraduate}{Graduate Student Instructor (Primary Instructor: Nicholas Valentino)}
    \end{tablist}
    
    
    \section*{Service to the Field}
    \subsection*{Academic Peer Review}
    
    \begin{itemize}
        \item[] \emph{American Political Science Review}
        \item[] \emph{JPART}
        \item[] \emph{The Journal of Politics}
        \item[] \emph{American Journal of Political Science}
        \item[] \emph{Politics \& Gender}
    \end{itemize}
    
    \section*{Departmental Service}
    
    \subsection*{University of California San Diego}
    \begin{tablist}
        \item[2021-] \tab{}Law and Policy Ad Hoc Exploratory Committee.
        \item[2020-] \tab{}Admission's Committee.
    \end{tablist}
    
    \subsection*{Harvard University}
    \begin{tablist}
        \item[2015-17] \tab{}Graduate Student Coordinator, Undergraduate Research Scholars Program, Institute for Quantitative Social Science.
    \end{tablist}
    
    

    
    
    \section*{Memberships}
    
    \begin{itemize}
    \item American Political Science Association
    \item Midwest Political Science Association
    \item Southern Political Science Association
    \item American Law and Economics Association    
    \end{itemize}
    
    \section*{Professional Employment}

    \begin{tablist}
    \item[2014] \tab{}Summer Law Clerk. UNC School of Government. Chapel Hill, North Carolina.
    \item[2014] \tab{}Summer Associate. Paul Hastings LLP. New York, NY.
    \item[2013] \tab{}Summer Law Clerk to Chief Judge Beryl Howell. US District Court. Washington, DC. 
    \item[2011-12] \tab{}Polling Analyst. Obama for America Reelection Campaign. Chicago, IL.
    \end{tablist}
    
    \section*{Consulting}
    \begin{tablist}
    \item[2020] \tab{}M4BL: The Movement for Black Lives. Advised on sections of the BREATHE ACT.
    \item[2019] \tab{}Cleveland County, North Carolina. Advised on anti-subsidy doctrines in US Constitutional law.
    \end{tablist}


    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
