
    \section*{Invited Talks}

    \begin{tablist}
    \talk{2024}{White Shoes, Hidden Hands}{Emory University, Department of Political Science}{Feb 8}
    \talk{2023}{Lawyers as Lobbyists}{Yale University. Department of Political Science}{Feb 1}
	\talk{2022}{Making Regulators Reasonable}{University of Michigan Law School}{Mar 24}
	
    \talk{2021}{Making Regulators Reasonable}{Hebrew University. Department of Political Science}{Dec 15}
    	
	\talk{2021}{Making Regulators Reasonable}{Tel Aviv University. Department of Political Science}{Dec 13}
			
	\talk{2021}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Northwestern University. Department of Political Science}{Nov 2}
		
    \talk{2020}{Agency Failure and Individual Accountability}{Georgetown University. Department of Government}{Jan 24}
    %
    \talk{2020}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{University of Texas, Austin. McCombs School of Business}{Jan 8}
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Stanford University. Hoover Institution}{Dec 6}
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Vanderbilt University. Department of Political Science}{Nov 13}
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{University of California, San Diego. School of Global Policy and Strategy}{Nov 6}
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Harvard Law School}{Nov 5}    
    %
    \talk{2019}{Agency Failure and Individual Accountability}{George Mason Law School}{Sep 19}
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Washington University in St. Louis. Department of Political Science}{Sep 17}    
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Berkeley Law School. Jurisprudence and Social Policy Program}{Feb 7}    
    %
    \talk{2019}{Meetings, Comments, and the Distributive Politics of Administrative Policymaking}{Harvard Business School. Business Government and International Economy Unit}{Nov 5}   
    % 
    \talk{2019}{The Gains from Lobbying Financial Regulators}{Administrative Conference of the United States}{Aug 9}    
    %
    \talk{2018}{What’s at Stake in Rulemaking? Financial Market Evidence for Banks’ Influence on Administrative Agencies}{University of Texas, Austin. McCombs School of Business}{Mar 23}
    
    \end{tablist}